Classless Java: Tuning Java Interfaces

### 2015-11-25 paper/sections/CaseStudy.tex
Future Work ready for review.

\subsection{A Small Game Example}
We now present a variant of a classic game example, which is often used to
evaluate code reuse ability related to inheritance and design patterns. The code
using our approach and the solution by Bono et. al~\cite{bono14} in online, for
space constraints, we will omit it here. In the game, there is a player with the
goal of collecting as many coins as possible. She may enter a room with several
doors to be chosen among. This is a good example because it involves code reuse
(different kinds of doors inherit a common type, with different features and
behaviour), multiple inheritance (a special kind of door may require features
from two other door types) and it also shows how to model operations
\texttt{symmetric sum}, \texttt{override} and \texttt{alias} as trait-oriented
programming. Moreover, the code is provided in ~\cite{bono14} so that we can
have a clear and fair comparison with our approach, as shown in
Table~\ref{table:codereduction}. We reduced the interfaces/classes used by
21.4\% (from 14 to 11) due to the replacement of instantiation classes with
generated \texttt{of} methods. We reduced source lines of code (SLOC) by
40\%. To ensure a fair comparison, we use the same code style as Bono's.

>>>>

\subsection{A Small Game Example}
We now present a variant of a classic game example, which is used to
evaluate code reuse ability related to inheritance and design patterns. The code
using our approach and the solution by Bono et. al~\cite{bono14} in online, for
space constraints, we will omit it here. In the game, there is a player with the
goal of collecting as many coins as possible. She may enter a room with several
doors to be chosen among. This is a good example because it involves code reuse
(different kinds of doors inherit a common type, with different features and
behaviour), multiple inheritance (a special kind of door may require features
from two other door types) and it also shows how to model operations
\texttt{symmetric sum}, \texttt{override} and \texttt{alias} as trait-oriented
programming. Moreover, the code is provided in ~\cite{bono14} so that we can
have a clear and fair comparison with our approach, as shown in
Table~\ref{table:codereduction}. We reduced the interfaces/classes used by
21.4\% (from 14 to 11) due to the replacement of instantiation classes with
generated \texttt{of} methods. We reduced source lines of code (SLOC) by
40\%. To ensure a fair comparison, we use the same code style as Bono's.
